Verifying Demonstrations

### 2018-05-23 paper/properties.tex
Finishes editing of properties

We note that we cannot actually improve the privacy of participating protesters during the protest: if Alice is caught during a protest or other crowd-counting mechanisms based on photographic or video evidence are used to identify Alice, there is nothing we can do.
\seb{suggestion maybe we should put the following part in the discussion}
However, in \PRIVO, we aim at verifiable participation count that does not add any threats to the participants' privacy. 
For instance, if there are counter-protests in the \emph{same location at the same time}, Alice could even blend into another crowd and argue that she participated in a different protest than she actually did --- and the counts would still be correct afterwards.
However, even if there is only one protest and she is not caught in the act, then using our proposed mechanism should not incur any additional risk.
Thus we need at least participation-proof privacy but receipt freeness is also desired.
In essence, this means that upon completing the protocol, Eve cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
\sonja{I'm confused: can we or can we not provide this?}
\seb{I agree with Sonja, it is not clear whether we achieve it or not}

\subsubsection{Participation-proof privacy}

\begin{definition}[Proof indistinguishability]
  Adversary chooses two messages \(m_0, m_1\) and gives them to the challenger.
  Challenger uniformly randomly selects \(b\rgets \bin\) and runs \(c_b \gets 
    PRF_k(m_0), c_{1-b} \gets PRF_k(m_1)\).
  The challenger gives \(c_0, c_1\) to adversary.
  If the adversary outputs \(b' = b\) she wins.
  (The property should be similar to key privacy~\cite{KeyPrivacy}.)
\end{definition}

\subsubsection{Receipt freeness}

\begin{definition}[Receipt freeness/deniability]
  Adversary gets oracle access to the user?
  User provides a witness?
\end{definition}

>>>>

This leaves us with what should correspond to vote privacy.
We need unlinkability between Alice's identity and Alice's participation proof.
Given a participation proof, Grace will not be able to tell if it belongs to 
Alice or Bob.
This is stronger than vote privacy, where Grace may know that Alice voted but 
not what she voted, whereas here she may not know whether Alice \enquote{voted} 
or not.
Thus participants and non-participants must be indistinguishable.
As this is quite difficult to achieve, we settle for something slightly weaker:
\begin{requirements}[P]
\item\label{ProtestInd} Participants of two different protests must be 
  indistinguishable.
\end{requirements}
Thus Alice can always argue to be part of any counter-protest while actually 
supporting the protest, which, in fact, is a slight increase in privacy over 
ordinary protests.
